---
title: "Lab 2 Pt2"
output: html_document
---

> Let's apply some of the syntax we've learned this week to some problems.
> This should be similar to Problem Set 1, but be warned that the data is different.

---

Your problem set is based on resources produced by Elena Llaudet and Kosuke Imai. It draws on the data and research in the following publication:

Raghabendra Chattopadhyay and Esther Duflo. 2004. “Women as Policy Makers: Evidence from a
Randomized Policy Experiment in India." Econometrica, 72 (5): 1409–43.)

Today our data will be completely made up. The scenario is as follows:

I hypothesize that the ingestion of spiders while asleep **causes** individuals' propensity to buy blind boxes to increase. To tes this, I survey some number of individuals in my neighborhood, collecting data on:

1) `adult`: whether they are an adult. `=1` if yes and `=0` if no.
2) `spiders`: how many spiders they ingested in their sleep the previous week.
3) `blindbox`: how many blindboxes they bought this week.

---

# Getting Started

Read the CSV file ["lab2data.csv"](https://github.com/yuanzhouwang/yzwang-teaching/blob/main/lab2data.csv) into an object called `df`. Read the first few observations of the dataset.

```{r}
# df <- read.csv("lab2data.csv")
# head("lab2data.csv")
```


-   What does each observation in this dataset represent?
-   Please substantively interpret the first observation in the dataset.
-   What is the **type** of each variable in the dataset?

---

# Exploratory Data Analaysis

Please provide your code for the following statistics:

-   How many observations are in the dataset?
-   What percent of survey respondents were adults?
-   On average, how many spiders did respondents ingest the previous week?

```{r}
# dim(df)[1]
# nrow(df) # This also works
# mean(df$adult)
# mean(df$spiders)
```


---

# Methodology
We want to estimate the *average causal effect* of ingesting spiders on buying blind boxes.

1) What would be the treatment variable?
2) What would be the outcome variable?
3) What would be the treatment group?
4) What would be the control group?

We also wanted to estimate the average causal effect of being an adult on the propensity to buy blind boxes:

1) What would be the treatment variable?
2) What would be the outcome variable?
3) What would be the treatment group?
4) What would be the control group?